SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-27 quiz.tex
Occurence

\begin{table}[t]
\caption{Quiz question templates with examples. When not otherwise noted, distractors are wrong answers that are neighbors of degree at most 2 of the correct answer.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Subject}		&Ask for the subject of a (subject, relation, object) triple given the relation and object.\\
%						&Distractors are labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object but which are connected to the correct answer with a path of length at most 2.\\
Stem					&\emph{Who is \emph{responsible for} \emph{Medical Admission}?}\\
Key						&\emph{Physician}\\
Distractors				&\emph{Surgeon}, \emph{Health Care Professional}, \emph{Senior Physician}\\
\midrule
\textbf{Object}			&Ask for the object of a (subject, relation, object) triple given the subject and relation.\\
Stem					&\emph{The \emph{Specification Team} is \emph{responsible for}}$\ldots$\\
Key						&\emph{Functional Specification Document}\\
Distractors: 			&\emph{Project Team Member}, \emph{Sponsor}, \emph{Defining Project Organization}\\
\midrule
\textbf{Definition}		&Ask for the class that fits the given textbook definition.\\
Stem					&\emph{What is defined by this?}\\
						&\enquote{X assures a defined quality of all processes and outcomes of the hospital}\\
Key						&\emph{Internal Quality Management}\\
Distractors				&\emph{Activity}, \emph{Complaint}, \emph{Diagnosis}\\
\midrule
\textbf{Intertwined}	&The correct answer is a triangle in the graph. The distractors instead form different shapes based on the difficulty. See \cref{fig:intertwined}.\\
Stem					&In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Key						&\emph{Chief Information Officer -- Department of Information management -- IM Staff}\\
Distractor 1			&\emph{Chief Information Officer -- Strategic Gap -- Corporate Strategy}\\
Distractor 2			&\emph{Chief Information Officer -- Ticket Evaluation -- Project Monitoring}\\
\midrule
\textbf{CloseMatch}		&\\
Stem \\
Key \\
Distractors \\
\midrule
\textbf{Label-Definition}	&Present different definitions and ask, which of them fits the given entity.\\
Stem					&\emph{How is \enquote{Chief Executive Officer} defined?}\\
Key						&\emph{Responsible for setting and carrying out the strategic plans and policies of an enterprise.}\\
Distractors				&labels of entities within a path length of at most 2, e.g. \emph{Anyone who has direct or indirect influence on or interest in a component of an information system.}\\
\midrule
\textbf{}				&\\
						&Stem: \\
Example:				&Key: \\
						&Distractors: \\
\bottomrule
\end{tabulary}
\end{table}

>>>>

\begin{table}[t]
\caption{Quiz question templates with examples. When not otherwise noted, distractors are wrong answers that are neighbors of degree at most 2 of the correct answer.}
\label{tab:templates}
\centering
\begin{tabulary}{\columnwidth}{lL}
\toprule
\textbf{Template}	&\textbf{Description}\\
\midrule
\textbf{Subject}		&Ask for the subject of a (subject, relation, object) triple given the relation and object.\\
%						&Distractors are labels of other classes (of the same type) that \emph{are not} related via the same relation to the same object but which are connected to the correct answer with a path of length at most 2.\\
Stem					&\emph{Who is \emph{responsible for} \emph{Medical Admission}?}\\
Key						&\emph{Physician}\\
Distractors				&\emph{Surgeon}, \emph{Health Care Professional}, \emph{Senior Physician}\\
\midrule
\textbf{Object}			&Ask for the object of a (subject, relation, object) triple given the subject and relation.\\
Stem					&\emph{The \emph{Specification Team} is \emph{responsible for}}$\ldots$\\
Key						&\emph{Functional Specification Document}\\
Distractors: 			&\emph{Project Team Member}, \emph{Sponsor}, \emph{Defining Project Organization}\\
\midrule
\textbf{Definition}		&Ask for the class that fits the given textbook definition.\\
Stem					&\emph{What is defined by this?}\\
						&\enquote{X assures a defined quality of all processes and outcomes of the hospital}\\
Key						&\emph{Internal Quality Management}\\
Distractors				&\emph{Activity}, \emph{Complaint}, \emph{Diagnosis}\\
\midrule
\textbf{Intertwined}	&The correct answer is a triangle in the graph. The distractors are of different shapes based on the difficulty. See \cref{fig:intertwined}.\\
Stem					&In the context of Strategic Information Management, which one of the following triples belongs together the most?\\
Key						&\emph{Chief Information Officer -- Department of Information management -- IM Staff}\\
Distractor 1			&\emph{Chief Information Officer -- Strategic Gap -- Corporate Strategy}\\
Distractor 2			&\emph{Chief Information Officer -- Ticket Evaluation -- Project Monitoring}\\
\midrule
\textbf{Close-By}		&\\
Stem \\
Key \\
Distractors \\
\midrule
\textbf{Label-Definition}	&Present different definitions and ask, which of them fits the given entity.\\
Stem					&\emph{How is \enquote{Chief Executive Officer} defined?}\\
Key						&\emph{Responsible for setting and carrying out the strategic plans and policies of an enterprise.}\\
Distractors				&labels of entities within a path length of at most 2, e.g. \emph{Anyone who has direct or indirect influence on or interest in a component of an information system.}\\
\midrule
\textbf{Occurence}				& Asks where a term is set to exist in the used ontologies of SNIK. These ontologies are made up of relations based on the books \cite{ob} and \cite{bb}.\\
						&Stem:  In which contexts does the term \enquote{Health Insurance Company} occur? \\
Example:				&Key: Strategic Information Management \\
						&Distractor 1: Tactical Information Management \\
						&Distractor 2: Both Contexts \\
						&Distractor 3: Neither \\
\bottomrule
\end{tabulary}
\end{table}
